SDSS-IV MaNGA: The Radial Profile of Enhanced Star Formation in Close Galaxy Pairs

### 2021-02-04 build/final_submit_v3/maintex.tex
added final submit folder

\linenumbers
% Units
\newcommand{\kms}{km~s$^{-1}$}
\newcommand{\msun}{$M_{\odot}$}
\newcommand{\msunyr}{$M_{\odot}~{\rm yr}^{-1}$}
\newcommand{\lsun}{$L_{\odot}$}
\newcommand{\ergs}{erg~s$^{-1}$}
\newcommand{\cmsq}{cm$^{-2}$}
\newcommand{\um}{$\mu$m}
\newcommand{\uJy}{$\mu$Jy}
\newcommand{\sqdeg}{deg$^2$}
\newcommand{\lx}{$L_{\rm X}$}
\newcommand{\lmir}{$L_{\rm 12\mu m}$}
\newcommand{\loiii}{$L_{\rm [OIII]}$}
% Emission lines
\newcommand{\Ha}{H$\alpha$}
\newcommand{\Hb}{H$\beta$}
\newcommand{\OII}{[O\,{\sc ii}]}
\newcommand{\OIIlam}{[O\,{\sc ii}]\,$\lambda$3727}
\newcommand{\SII}{[S\,{\sc ii}]}
\newcommand{\OIII}{[O\,{\sc iii}]}
\newcommand{\OIIIlam}{[O\,{\sc iii}]\,$\lambda$5007}
\newcommand{\NII}{[N\,{\sc ii}]}
\newcommand{\NeIII}{[Ne\,{\sc iii}]}
% special 
\newcommand{\reff}{$R_{\rm eff}$}
\newcommand{\ewha}{EW(H$\alpha$)}
\newcommand{\logm}{log($M/M_{\odot}$)}
\defcitealias{Fu:2018}{Paper I}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\centering
\includegraphics[width=\linewidth]{bpt-cmd.pdf}
\caption[]{(\textbf{Left}) Color-magnitude diagram for MaNGA galaxies. (\textbf{Center}) BPT diagram for the MaNGA galaxies. (\textbf{Right}) The WHAN diagram for the MaNGA galaxies. The grey circles represent the whole MaNGA sample and the color scale reflects the local density around each data point in this color-magnitude plane, as indicated by the color bar on the top. The {\it purple} diamonds represent the paired galaxies which are classified as retired (by the \ewha\ cut), the {\it blue} diamonds represent the star forming paired galaxies (by the BPT diagram), the {\it green} diamonds represent the composite star forming-AGN paired galaxies (by the BPT diagram), and the {\it Red} diamonds represent the paired galaxies containing an AGN (by the BPT diagram).}
\label{fig:cmd}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

The MaNGA sample does not have a uniform spatial coverage, 63\% of the sample is designed to cover 1.5 \reff\ (the Primary+ subsample) and 37\% of the sample is designed to cover 2.5 \reff\ (the Secondary subsample). This means that there will be fewer selected spaxels beyond 1.5 \reff\ and the S/N of the selected spaxels will be lower than those within 1.5 \reff. {\bf We decide to still extend our radial profiles out to 2.5 \reff\ to make full use of the MaNGA data; however, we emphasize that the difference in the sampling of the data within 1.5 \reff\ and the data beyond 1.5 \reff\ may create artificial slopes in the data. }

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\centering
\includegraphics[width=\linewidth]{ssfr_comb.pdf}
\caption[]{The log(sSFR) as a function of galactocentric radius for control galaxies (\textbf{Left}) and galaxy pairs (\textbf{Middle}). The difference between the profiles of the paired galaxies and the control galaxies are shown in the \textbf{Right} panel. The dashed black profile represents the mean of the difference profiles. The colors of the profiles represent the mass range of the selected galaxies which is given in the legend along with the number of galaxies in that mass bin in parantheses. The highlighted region around the profiles represent the standard error of the mean of the data at the given radius interval. {\bf The vertical dash-dot line marks 1.5 \reff, beyond which the radial sampling is expected to fall.}}
\label{fig:ssfr_prof}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\centering
\includegraphics[width=0.8\linewidth]{ssfr_mass.pdf}
\caption[]{The \textbf{Left} panel shows the $\Delta$log(sSFR) profiles where the difference profiles are constructed from the difference between the paired galaxy profiles and a set of 20 control galaxies. The profiles are split into five different stellar mass bins and the highlighted region about the profiles represent the standard error of mean of the profile. The black dashed line represents the mean profile between the four difference mass ranges. The number of paired galaxies in each mass range is given in the legend in parentheses. The \textbf{Right} panel shows the nuclear $\Delta$log(sSFR) extracted from a 0.5\reff\ aperture. The black squares are the mean values within a stellar mass bin (where the size of the bins are shown the the horizontal error bars). The vertical error bars on the black squares represent the standard deviation within the bin. The horizontal, dashed black line represents the median central enhancement of the pair sample. Galaxies in the outside-IFU (Blue) and inside-IFU (Red) samples are separately depicted. {\bf The vertical dash-dot line marks 1.5 \reff, beyond which the radial sampling is expected to fall. }
}
\label{fig:ssfr_mass}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\subsubsection{Tailored-Controls Difference Profiles}\label{sec:tailored}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\centering
\includegraphics[width=0.8\linewidth]{ssfr_dm.pdf}
\caption[]{Same as Figure \ref{fig:ssfr_mass} except the difference profiles are split by the mass ratio of the pair. The \textbf{top} row is the absolute value of the mass ratio and the \textbf{bottom} row is the mass ratio without taking the absolute value. Taking the mass ratio without the absolute value allows us to separately study the more massive companions of pairs from the less massive companions from pairs. The inside-IFU sample is left out of this analysis because we do not yet have reliable measurements of their total stellar mass ratios.}
\label{fig:ssfr_dm}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
In the second method, we match each paired galaxy to a set of 20 control galaxies of similar stellar masses and redshifts, as described in \S~\ref{sec:control}. We then take the median of the azimuthally averaged profiles of the tailored control sample. Finally, we obtain the $\Delta\log$sSFR profile for each of the 169 paired galaxies by calculating the difference between its sSFR profile and the median profile of its control sample.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering
\includegraphics[width=3in]{prof_comp.pdf}
\caption[]{The mean radial profile of $\Delta$log(sSFR) (\textbf{Top}) and $\Delta$log(SFR) (\textbf{Bottom}) between pairs and controls of this work with the tailored control method ({\it Black}) compared against those of \citet{Pan:2019} ({\it Red}), a pair sample, and \citet{Thorp:2019} ({\it Blue}), a post-merger sample.}
\label{fig:prof_comp}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering
\includegraphics[width=3in]{nuc_sep.pdf}
\caption[]{(\textbf{Top}) $\Delta$log(SFR) \textbf{extracted from the inner 0.5 \reff} over projected separation from this study ({\it Black}), \citet{Ellison:2008} ({\it Red}), \citet{Scudder:2012} ({\it Blue}), \citet{Patton:2013} ({\it Green}), and \citet{Bustamante:2020} ({\it Purple}). (\textbf{Bottom}) $\Delta$log(sSFR) extracted from the inner 0.5 \reff over projected separation from this study ({\it Black}), \citet{Li:2008} ({\it Red}), and \citet{Patton:2020} ({\it Blue}).
}
\label{fig:nuc_sep}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

We also find that there is a difference in the $\Delta$log(sSFR) offsets at wide radii between primary and secondary companions. The primary companion features an enhancement to their sSFR at wide radii while the secondary companion features a suppression to their sSFR at wide radii. The reason for this is unclear; however, this means that the primary companions will experience enhanced stellar mass growth across their disks while the secondary companions will see only see substantial stellar mass growth in their centers which will result in more bulge dominated galaxies. {\bf Differences in the bulge-to-total ratio, (B/T), has been observed in previous works like \citet{Bluck:2019} who found that satellites tend to have slighter higher (B/T) ratios in comparison to central galaxies at the same stellar mass.}

>>>>

%\linenumbers
% Units
\newcommand{\kms}{km~s$^{-1}$}
\newcommand{\msun}{$M_{\odot}$}
\newcommand{\msunyr}{$M_{\odot}~{\rm yr}^{-1}$}
\newcommand{\lsun}{$L_{\odot}$}
\newcommand{\ergs}{erg~s$^{-1}$}
\newcommand{\cmsq}{cm$^{-2}$}
\newcommand{\um}{$\mu$m}
\newcommand{\uJy}{$\mu$Jy}
\newcommand{\sqdeg}{deg$^2$}
\newcommand{\lx}{$L_{\rm X}$}
\newcommand{\lmir}{$L_{\rm 12\mu m}$}
\newcommand{\loiii}{$L_{\rm [OIII]}$}
% Emission lines
\newcommand{\Ha}{H$\alpha$}
\newcommand{\Hb}{H$\beta$}
\newcommand{\OII}{[O\,{\sc ii}]}
\newcommand{\OIIlam}{[O\,{\sc ii}]\,$\lambda$3727}
\newcommand{\SII}{[S\,{\sc ii}]}
\newcommand{\OIII}{[O\,{\sc iii}]}
\newcommand{\OIIIlam}{[O\,{\sc iii}]\,$\lambda$5007}
\newcommand{\NII}{[N\,{\sc ii}]}
\newcommand{\NeIII}{[Ne\,{\sc iii}]}
% special 
\newcommand{\reff}{$R_{\rm eff}$}
\newcommand{\ewha}{EW(H$\alpha$)}
\newcommand{\logm}{log($M/M_{\odot}$)}
\defcitealias{Fu:2018}{Paper I}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\centering
\includegraphics[width=\linewidth]{bpt-cmd.pdf}
\caption[]{(Left) Color-magnitude diagram for MaNGA galaxies. (Center) BPT diagram for the MaNGA galaxies. (Right) The WHAN diagram for the MaNGA galaxies. The grey circles represent the whole MaNGA sample and the color scale reflects the local density around each data point in this color-magnitude plane, as indicated by the color bar on the top. The {\it purple} diamonds represent the paired galaxies which are classified as retired (by the \ewha\ cut), the {\it blue} diamonds represent the star forming paired galaxies (by the BPT diagram), the {\it green} diamonds represent the composite star forming-AGN paired galaxies (by the BPT diagram), and the {\it Red} diamonds represent the paired galaxies containing an AGN (by the BPT diagram).}
\label{fig:cmd}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

The MaNGA sample does not have a uniform spatial coverage, 63\% of the sample is designed to cover 1.5 \reff\ (the Primary+ subsample) and 37\% of the sample is designed to cover 2.5 \reff\ (the Secondary subsample). This means that there will be fewer selected spaxels beyond 1.5 \reff\ and the S/N of the selected spaxels will be lower than those within 1.5 \reff. We decide to still extend our radial profiles out to 2.5 \reff\ to make full use of the MaNGA data; however, we emphasize that the difference in the sampling of the data within 1.5 \reff\ and the data beyond 1.5 \reff\ may create artificial slopes in the data.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\centering
\includegraphics[width=\linewidth]{ssfr_comb.pdf}
\caption[]{The log(sSFR) as a function of galactocentric radius for control galaxies (Left) and galaxy pairs (Middle). The difference between the profiles of the paired galaxies and the control galaxies are shown in the Right panel. The dashed black profile represents the mean of the difference profiles. The colors of the profiles represent the mass range of the selected galaxies which is given in the legend along with the number of galaxies in that mass bin in parantheses. The highlighted region around the profiles represent the standard error of the mean of the data at the given radius interval. The vertical dash-dot line marks 1.5 \reff, beyond which the radial sampling is expected to fall.}
\label{fig:ssfr_prof}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\centering
\includegraphics[width=0.8\linewidth]{ssfr_mass.pdf}
\caption[]{The Left panel shows the $\Delta$log(sSFR) profiles where the difference profiles are constructed from the difference between the paired galaxy profiles and a set of 20 control galaxies. The profiles are split into five different stellar mass bins and the highlighted region about the profiles represent the standard error of mean of the profile. The black dashed line represents the mean profile between the four difference mass ranges. The number of paired galaxies in each mass range is given in the legend in parentheses. The Right panel shows the nuclear $\Delta$log(sSFR) extracted from a 0.5\reff\ aperture. The black squares are the mean values within a stellar mass bin (where the size of the bins are shown the the horizontal error bars). The vertical error bars on the black squares represent the standard deviation within the bin. The horizontal, dashed black line represents the median central enhancement of the pair sample. Galaxies in the outside-IFU (Blue) and inside-IFU (Red) samples are separately depicted. The vertical dash-dot line marks 1.5 \reff, beyond which the radial sampling is expected to fall. 
}
\label{fig:ssfr_mass}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\subsubsection{Tailored-Controls Difference Profiles}\label{sec:tailored}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\centering
\includegraphics[width=0.8\linewidth]{ssfr_dm.pdf}
\caption[]{Same as Figure \ref{fig:ssfr_mass} except the difference profiles are split by the mass ratio of the pair. The top row is the absolute value of the mass ratio and the bottom row is the mass ratio without taking the absolute value. Taking the mass ratio without the absolute value allows us to separately study the more massive companions of pairs from the less massive companions from pairs. The inside-IFU sample is left out of this analysis because we do not yet have reliable measurements of their total stellar mass ratios.}
\label{fig:ssfr_dm}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
In the second method, we match each paired galaxy to a set of 20 control galaxies of similar stellar masses and redshifts, as described in \S~\ref{sec:control}. We then take the median of the azimuthally averaged profiles of the tailored control sample. Finally, we obtain the $\Delta\log$sSFR profile for each of the 169 paired galaxies by calculating the difference between its sSFR profile and the median profile of its control sample.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering
\includegraphics[width=3in]{prof_comp.pdf}
\caption[]{The mean radial profile of $\Delta$log(sSFR) (Top) and $\Delta$log(SFR) (Bottom) between pairs and controls of this work with the tailored control method ({\it Black}) compared against those of \citet{Pan:2019} ({\it Red}), a pair sample, and \citet{Thorp:2019} ({\it Blue}), a post-merger sample.}
\label{fig:prof_comp}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering
\includegraphics[width=3in]{nuc_sep.pdf}
\caption[]{(Top) $\Delta$log(SFR) extracted from the inner 0.5 \reff over projected separation from this study ({\it Black}), \citet{Ellison:2008} ({\it Red}), \citet{Scudder:2012} ({\it Blue}), \citet{Patton:2013} ({\it Green}), and \citet{Bustamante:2020} ({\it Purple}). (Bottom) $\Delta$log(sSFR) extracted from the inner 0.5 \reff over projected separation from this study ({\it Black}), \citet{Li:2008} ({\it Red}), and \citet{Patton:2020} ({\it Blue}).
}
\label{fig:nuc_sep}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

We also find that there is a difference in the $\Delta$log(sSFR) offsets at wide radii between primary and secondary companions. The primary companion features an enhancement to their sSFR at wide radii while the secondary companion features a suppression to their sSFR at wide radii. The reason for this is unclear; however, this means that the primary companions will experience enhanced stellar mass growth across their disks while the secondary companions will see only see substantial stellar mass growth in their centers which will result in more bulge dominated galaxies. Differences in the bulge-to-total ratio, (B/T), has been observed in previous works like \citet{Bluck:2019} who found that satellites tend to have slighter higher (B/T) ratios in comparison to central galaxies at the same stellar mass.
